### 2016-08-17 Appendix.tex
changes after submission

\begin{scope}[shift={(1,-8)}]
	\node at (-1.5,0.7) {\circled{8}};
	\draw[fermion] (0,0)--(45:1);
	\draw[fermionbar] (0,0)--(-45:1);
	\draw[gluon] (0,0)--(180:1);
	\node at (45:1.3) {$\overline{q}i$};
	\node at (-45:1.3) {$q_j$};
	\node at (180:1.3) {$G_\mu^a$};
	\node at (2,0) {$\hat{=} -ig_s T^a_{ij}\gamma^\mu$};
\end{scope}
\begin{scope}[shift={(8,-8)}]
	\node at (-1.5,0.7) {\circled{9}};
	\draw[scalar] (0,0)--(45:1);
	\draw[scalarbar] (0,0)--(-45:1);
	\draw[gluon] (0,0)--(180:1);
	\node at (45:1.4) {$\tilde{q}^\dagger_{Ai}(-p_1)$};
	\node at (-45:1.4) {$\tilde{q}_{Bj}(p_2)$};
	\node at (180:1.3) {$G_\mu^a$};
	\node at (3,0) {$\hat{=} -ig_s (p_2+p_1)^\mu T^a_{ij}\delta_{AB}$};
\end{scope}
\begin{scope}[shift={(1,-10.5)}]
	\node at (-1.5,0.7) {\circled{10}};
	\draw[scalar] (0,0)--(45:1);
	\draw[scalarbar] (0,0)--(-45:1);
	\draw[gluon] (0,0)--(135:1);
	\draw[gluon] (0,0)--(-135:1);
	\node at (45:1.4) {$\tilde{q}^\dagger_{Ai}$};
	\node at (-45:1.4) {$\tilde{q}_{Bj}$};
	\node at (135:1.4) {$G_\mu^a$};
	\node at (-135:1.4) {$G_\nu^b$};
	\node at (3,0) {$\hat{=} \ ig_s^2 g^{\mu\nu} \left\{T^a,T^b\right\}_{ij}\delta_{AB}$};
\end{scope}
\begin{scope}[shift={(1,-13.5)}]
	\node at (-1.5,0.7) {\circled{11}};
	\draw[gluon] (0,0)--(45:1);
	\draw[gluon] (0,0)--(-45:1);
	\draw[gluon] (0,0)--(180:1);
	\node at (45:1.4) {$G_\mu^a(p_a)$};
	\node at (-45:1.4) {$G_\nu^b(p_b)$};
	\node at (180:1.5) {$G_\rho^c(p_c)$};
	\node at (5.5,0) {$\hat{=}  - g_s f_{abc} \left[ g_{\mu\nu}(p_a-p_b)^\rho +\  g_{\nu\rho}(p_b-p_c)^\mu +  g_{\rho\mu}(p_c-p_a)^\nu \right]$};
\end{scope}
\end{tikzpicture}
\caption{In the Feynman diagrams of the propagators the momentum is flowing from the right to the left hand side. The gluon propagator is given in Feynman gauge.\newline
In the Feynman diagrams of the vertices all momenta flow towards the vertex, i.e. in diagram 9: $-p_1$ flows towards the vertex.\newline
The indices $A,B \in \left\{ L,R \right\}$ label the left/right ``handedness'' of the squarks. The indices $i,j=1,2,3$ are the color indices in the (anti)fundamental representation where $a,b,c,\hdots = 1,\hdots,8$ are the color indices of the adjoint representation.}\label{fig:firstFeynmanRules}
\end{center}
\end{figure}
\newpage

@@

The definition of the momenta within the Passarino-Veltman integrals in this thesis agrees with the one from \texttt{Looptools} \cite{Hahn:1998} convention. The original paper \cite{Passarino:1978jh} uses slightly different conventions. A pedagogical introduction to the evaluation of one-loop integrals can be found in \cite{Ellis:2011cr}.  $A$, $B$ and $C$ integrals are defined by:

@@

\frac{i}{16\pi^2} A_0(m^2) &= \int_l \frac{1}{l^2-m^2},\nonumber\\
\frac{i}{16\pi^2} B_{0,\mu,\mu\nu}(p^2,m_1^2,m_2^2) &= \int_l \frac{\left\{1,l_\mu,l_\mu l_\nu \right\}}{[l^2-m_1^2][(l+p)^2-m_2^2]},\\
\frac{i}{16\pi^2} C_{0,\mu,\mu\nu}(p_1^2,p_2^2,(p_1+p_2)^2,m_1^2,m_2^2,m_3^2) &= \int_l \frac{\left\{1,l_\mu,l_\mu l_\nu \right\}}{[l^2-m_1^2][(l+p_1)^2-m_2^2][(l+p_1+p_2)^2-m_3^2]},\nonumber\label{eq:LoopInt}

@@

C_\mu &= p_{1\mu}C_1 + p_{2\mu}C_2,\\

@@

where the typical UV-divergent constant $\Delta_\epsilon = \frac{1}{\epsilon} - \gamma_E+\ln 4\pi$ is defined. It comprises the Euler-Mascheroni constant $\gamma_{\mathrm{E}}$. In the special case of vanishing momenta, the further integrals take a succinct form. Some formulae which are needed for the calculation of renormalization constants are

>>>>

\begin{scope}[shift={(1,-8)}]
	\node at (-1.5,0.7) {\circled{8}};
	\draw[fermion] (0,0)--(45:1);
	\draw[fermionbar] (0,0)--(-45:1);
	\draw[gluon] (0,0)--(180:1);
	\node at (45:1.3) {$\overline{q}_i$};
	\node at (-45:1.3) {$q_j$};
	\node at (180:1.3) {$G_\mu^a$};
	\node at (2,0) {$\hat{=} -ig_s T^a_{ij}\gamma^\mu$};
\end{scope}
\begin{scope}[shift={(8,-8)}]
	\node at (-1.5,0.7) {\circled{9}};
	\draw[scalar] (0,0)--(45:1);
	\draw[scalarbar] (0,0)--(-45:1);
	\draw[gluon] (0,0)--(180:1);
	\node at (45:1.4) {$\tilde{q}^\dagger_{Ai}(-p_1)$};
	\node at (-45:1.4) {$\tilde{q}_{Bj}(p_2)$};
	\node at (180:1.3) {$G_\mu^a$};
	\node at (3,0) {$\hat{=} -ig_s (p_2+p_1)^\mu T^a_{ij}\delta_{AB}$};
\end{scope}
\begin{scope}[shift={(1,-10.5)}]
	\node at (-1.5,0.7) {\circled{10}};
	\draw[scalar] (0,0)--(45:1);
	\draw[scalarbar] (0,0)--(-45:1);
	\draw[gluon] (0,0)--(135:1);
	\draw[gluon] (0,0)--(-135:1);
	\node at (45:1.4) {$\tilde{q}^\dagger_{Ai}$};
	\node at (-45:1.4) {$\tilde{q}_{Bj}$};
	\node at (135:1.4) {$G_\mu^a$};
	\node at (-135:1.4) {$G_\nu^b$};
	\node at (3,0) {$\hat{=} \ ig_s^2 g^{\mu\nu} \left\{T^a,T^b\right\}_{ij}\delta_{AB}$};
\end{scope}
\begin{scope}[shift={(1,-13.5)}]
	\node at (-1.5,0.7) {\circled{11}};
	\draw[gluon] (0,0)--(45:1);
	\draw[gluon] (0,0)--(-45:1);
	\draw[gluon] (0,0)--(180:1);
	\node at (45:1.4) {$G_\mu^a(p_a)$};
	\node at (-45:1.4) {$G_\nu^b(p_b)$};
	\node at (180:1.5) {$G_\rho^c(p_c)$};
	\node at (5.5,0) {$\hat{=}  - g_s f_{abc} \left[ g_{\mu\nu}(p_a-p_b)^\rho +\  g_{\nu\rho}(p_b-p_c)^\mu +  g_{\rho\mu}(p_c-p_a)^\nu \right]$};
\end{scope}
\end{tikzpicture}
\caption{In the Feynman diagrams of the propagators the momentum is flowing from the right to the left hand side. The gluon propagator is given in Feynman gauge.\newline
In the Feynman diagrams of the vertices all momenta flow towards the vertex, i.e. in diagram 9: $-p_1$ flows towards the vertex.\newline
The indices $A,B \in \left\{ L,R \right\}$ label the left/right ``handedness'' of the squarks. The indices $i,j=1,2,3$ are the color indices in the (anti)fundamental representation where $a,b,c,\hdots = 1,\hdots,8$ are the color indices of the adjoint representation.}\label{fig:firstFeynmanRules}
\end{center}
\end{figure}
\newpage

@@

The definition of the momenta within the Passarino-Veltman integrals in this thesis agrees with the one from \texttt{Looptools} \cite{Hahn:1998}. The original paper \cite{Passarino:1978jh} uses slightly different conventions. A pedagogical introduction to the evaluation of one-loop integrals can be found in \cite{Ellis:2011cr}.  $A$, $B$ and $C$ integrals are defined by:

@@

\frac{i}{16\pi^2} A_0(m^2) &:= \int_l \frac{1}{l^2-m^2},\nonumber\\
\frac{i}{16\pi^2} B_{0,\mu,\mu\nu}(p^2,m_1^2,m_2^2) &:= \int_l \frac{\left\{1,l_\mu,l_\mu l_\nu \right\}}{[l^2-m_1^2][(l+p)^2-m_2^2]},\\
\frac{i}{16\pi^2} C_{0,\mu,\mu\nu}(p_1^2,p_2^2,(p_1+p_2)^2,m_1^2,m_2^2,m_3^2) &:= \int_l \frac{\left\{1,l_\mu,l_\mu l_\nu \right\}}{[l^2-m_1^2][(l+p_1)^2-m_2^2][(l+p_1+p_2)^2-m_3^2]},\nonumber\label{eq:LoopInt}

@@

C_\mu &:= p_{1\mu}C_1 + p_{2\mu}C_2,\\

@@

where the typical UV-divergent constant $\Delta_\epsilon = \frac{1}{\epsilon} - \gamma_E+\ln 4\pi$ is defined. It comprises the Euler-Mascheroni constant $\gamma_{\mathrm{E}}$. The relation between $\epsilon$ and the dimension $D$ is given by $D = 4-2\epsilon$. In the special case of vanishing momenta, the further integrals take a succinct form. Some formulae which are needed for the calculation of renormalization constants are

### 2016-08-17 Masterarbeit.tex
changes after submission

% abstract page
%\begin{center}\large\bfseries Summary\end{center}
\section*{\centering{Kurzdarstellung}}
Im Streben der Physik, die fundamentalen Bausteine der Natur zu beschreiben, stellt die Ent\-wicklung des Standardmodells der Teilchenphysik einen Meilenstein dar. Dieses beschreibt alle bekannten Elementarteilchen sowie deren nicht-gravitative Wechselwirkungen. Neben diesen Erfolgen ist aber auch bekannt, dass es unvollständig ist, da es keine Gravitation oder dunkle Materie beinhaltet. Supersymmetrie ist eine attraktive Erweiterung des Standardmodells, weil sie viele Probelme desselben auf eine elegante Weise löst.\\
Diese Arbeit untersucht eine supersymmetrische Erweiterung des Standardmodells welche zusätzlich $R$-symmetrisch ist. Neben der Berechnung von Wirkungsquerschnitten von stark wechelwirkenden supersymmetrischen Teilchen in der führenden Ordnung werden Einschleifen\-korrekturen zum Produktionswirkungsquerschnitt von Squarks in diesem Model berechnet und phenomenologisch ausgewertet.
\vspace{10em}
\section*{\centering{Abstract}}
In the ambition of understanding the fundamental mechanisms of nature, the Standard Model of particle physics constitutes a cornerstone in physics. It describes all known elementary particles and their non-gravitational interactions. Besides these successes it is known to be incomplete since it does not include gravity or dark matter. Supersymmetry is an attractive extension of the Standard Model as it solves many problems of it elegantly.\\
Within this thesis, a supersymmetric model which also exhibits $R$-symmetry is considered. Besides the calculation of tree-level cross sections for the production of strongly interacting supersymmetric particles, also one-loop corrections to the production cross section of squarks are calculated and phenomenologically analyzed.
\newpage

@@

%\appendix
\input{Appendix}
\newpage
\bibliography{references}
\newpage
\section*{\centering{Acknowledgements}}
First of all I like to thank Dominik Stöckinger who enthused me with theoretical particle physics and provided me with this interesting topic. In addition, he was always available for helping discussions whenever I was in need of them.\\
Special thanks go to Philip Dießner and Wojciech Kotlarski, who contributed significantly to results within this thesis. In addition I like to thank them, Markus Bach, Thomas Kwasnitza, Josua Unger and Tom Steudtner for many valuable discussions and support regarding physical questions as well as programming issues and a pleasant atmosphere in the office. Furthermore, I like to give them thanks for proofreading this thesis.\\
I am particularly grateful for Rebecca Schmidt's support within the last month which enabled me to focus on my thesis. In addition I like to thank her for proofreading.\\
Last but not least I would like to thank my family. Without them my physics studies would by no means have been possible in the way they were.
\newpage
% Erklärung
\clearpage
\thispagestyle{empty}
\minisec{Erklärung}\vspace*{1.5em}
Hiermit erkläre ich, dass ich diese Arbeit im Rahmen der Betreuung am Institut
für Kern- und Teilchenphysik ohne unzulässige Hilfe Dritter verfasst und alle Quellen als solche gekennzeichnet habe.
\vspace*{45em}
\par
Sebastian Liebschner\\
Dresden, Juli 2016

>>>>

% abstract page
%\begin{center}\large\bfseries Summary\end{center}
\section*{\centering{Kurzdarstellung}}
Im Streben der Physik, die fundamentalen Bausteine der Natur zu beschreiben, stellt die Ent\-wicklung des Standardmodells der Teilchenphysik einen Meilenstein dar. Dieses beschreibt alle bekannten Elementarteilchen sowie deren nicht-gravitative Wechselwirkungen. Neben diesen Erfolgen ist aber auch bekannt, dass es unvollständig ist, da es keine Gravitation oder dunkle Materie beinhaltet. Supersymmetrie ist eine attraktive Erweiterung des Standardmodells, weil sie viele Probleme desselben auf eine elegante Weise löst.\\
Diese Arbeit untersucht eine supersymmetrische Erweiterung des Standardmodells welche zusätzlich $R$-symmetrisch ist. Neben der Berechnung von Wirkungsquerschnitten von stark wechselwirkenden supersymmetrischen Teilchen in der führenden Ordnung werden Einschleifen\-korrekturen zum Produktionswirkungsquerschnitt von Squarks in diesem Modell berechnet und phenomenologisch ausgewertet.
\vspace{10em}
\section*{\centering{Abstract}}
In the ambition of understanding the fundamental mechanisms of nature, the Standard Model of particle physics constitutes a cornerstone in physics. It describes all known elementary particles and their non-gravitational interactions. Besides these successes it is known to be incomplete since it does not include gravity or dark matter. Supersymmetry is an attractive extension of the Standard Model as it solves many problems of it elegantly.\\
Within this thesis, a supersymmetric model which also exhibits $R$-symmetry is considered. Besides the calculation of tree-level cross sections for the production of strongly interacting supersymmetric particles, also one-loop corrections to the production cross section of squarks are calculated and phenomenologically analyzed.
\newpage

@@

%\appendix
\input{Appendix}
\newpage
\bibliography{references}
\newpage
\section*{\centering{Acknowledgements}}
First of all, I like to thank Dominik Stöckinger who enthused me with theoretical particle physics and provided me with this interesting topic. In addition, he was always available for helping discussions whenever I was in need of them.\\
Special thanks go to Philip Dießner and Wojciech Kotlarski, who contributed significantly to results within this thesis. In addition, I like to thank them, Markus Bach, Thomas Kwasnitza, Josua Unger and Tom Steudtner for many valuable discussions and support regarding physical questions as well as programming issues and a pleasant atmosphere in the office. Furthermore, I like to give them thanks for proofreading this thesis.\\
I am particularly grateful for Rebecca Schmidt's support within the last month which enabled me to focus on my thesis. In addition, I like to thank her for proofreading.\\
Last but not least, I would like to thank my family. Without them my physics studies would by no means have been possible in the way they were.
\newpage
% Erklärung
\clearpage
\thispagestyle{empty}
\minisec{Erklärung}\vspace*{1.5em}
Hiermit erkläre ich, dass ich diese Arbeit im Rahmen der Betreuung am Institut
für Kern- und Teilchenphysik ohne unzulässige Hilfe Dritter verfasst und alle Quellen als solche gekennzeichnet habe.
\vspace*{45em}
\par
Sebastian Liebschner\\
Dresden, Juli 2016

### 2016-08-17 NLO.tex
COMMITTED VERSION
changes after submission

The single pole is not that succinct and therefore not quoted here.

@@

For three different choices of $m_{\tilde{q}}$ and $m_{\tilde{g}}$, Philip Dießner checked the results up to permille accuracy by doing the calculation using \texttt{GoSam}\cite{Cullen:2014yla, Cullen:2011ac} and \texttt{MadGraph5\_aMC@NLO}\cite{Alwall:2014hca} on the basis of the same model file.\\
The next-to-leading order cross sections of this chapter bear a relative uncertainty of one percent due to the numerical integration. The uncertainty which corresponds to the variation of the scales $\mu_R$ and $\mu_F$, see section \ref{sec:tree-level_cross_sections}, are evaluate to around 15\%.

@@

\begin{table}[H]
\begin{center}
\begin{tabular}{c|c?c|c|c?c|c|c}
\multicolumn{2}{c?}{} & \multicolumn{3}{c?}{$p + p \to \tilde{u}_L + \tilde{u}_R$} & \multicolumn{3}{c}{$p + p \to \tilde{u} + \tilde{u}$} \\
\hlinewd{2pt}
$m_{\tilde{q}}$ in GeV & $m_{\tilde{g}}$ in GeV & $\sigma^{\mathrm{LO}}$ in fb & $\sigma^{\mathrm{NLO}}$ in fb & $K$ & $\sigma^{\mathrm{LO}}$ in fb & $\sigma^{\mathrm{NLO}}$ in fb & $K$\\
\hlinewd{2pt}
$500$ & $500$ & $966.4$ & $1328$ & $1.37$ & $2333$ & $3102$ \ignore{1328+2*887} & $1.33$\\
$500$ & $1000$ & $303.4$ & $352$ & $1.16$ & $1271$ & $1393$ \ignore{353 + 2*520} & $1.10$\\
$1000$ & $1000$ & $42.63$ & $58.5$ & $1.37$ & $122.2$ & $161.3$ \ignore{58.5+2*51.4} & $1.32$\\
$1000$ & $2000$ & $11.56$ & $13.3$ & $1.15$ & $66.36$ & $72.1$ \ignore{13.3+2*29.4} & $1.09$\\
$1500$ & $3000$ & $0.9166$ & $1.05$ & $1.14$ & $7.045$ & $7.57$\ignore{1.05+2*3.26} & $1.07$
\end{tabular}
\caption{$K$-factors of the process $pp \to \tilde{u}_L\tilde{u}_R$ and $pp \to \tilde{u}\tilde{u}$, where \mbox{$\tilde{u}\tilde{u} \in \left\{ \tilde{u}_L\tilde{u}_R, \tilde{u}_L\tilde{u}_L, \tilde{u}_R\tilde{u}_R \right\}$,} in the MSSM for a selected set of masses. The used parton density functions are the same as in table \ref{tab:MRSSMKfactors}.}\label{tab:KfactorsMSSM}
\end{center}
\end{table}
\begin{figure}[H]
\begin{center}
\includegraphics[scale=.6]{figures/Kfactor_MSSM.png}
\caption{Contour plot of the $K$-factor of the process  $pp \to \tilde{u}_L\tilde{u}_R$ and $pp \to \tilde{u}\tilde{u}$, where \mbox{$\tilde{u}\tilde{u} \in \left\{ \tilde{u}_L\tilde{u}_R, \tilde{u}_L\tilde{u}_L, \tilde{u}_R\tilde{u}_R \right\}$,} in the MSSM. The used parton density functions are the same as in table \ref{tab:MRSSMKfactors}.}\label{fig:Kfactor_MSSM}
\end{center}
\end{figure}
Again, it is clearly visible that the $K$-factors depend rather strongly on the ratio $\frac{m_{\mathrm{g}}}{m_{\mathrm{q}}}$ but not that strongly on the masses themselves (see also fig. \ref{fig:Kfactor_MSSM}). As the real corrections are identical to those in the MRSSM, it is again these very real corrections which are responsible for an enhancement of the $K$-factor for large values of  $\frac{m_{\mathrm{g}}}{m_{\mathrm{q}}}$.
Comparing with the results from the MRSSM in table \ref{tab:MRSSMKfactors}, one can state that the $K$-factors of the MRSSM are slightly larger. This might be the case, as there are additional degrees of freedom in the $R$-symmetric model, namely the octino which enters the gluino self-energy contributions (see second diagram from the right in fig. \ref{fig:GluinoSE}) and sgluons which enter box diagrams (see lower right diagram in fig. \ref{fig:1loopdiagrams}). The dependence on the sgluon mass is discussed within the next section.\\
The uncertainties of next-to-leading order cross sections, due to the phase space integration, within this section are of percent order. The uncertainty which corresponds to the scale variation does not exceed 15\%.

>>>>

The single pole does not take such a succinct form and is therefore not quoted here.

@@

For three different choices of $m_{\tilde{q}}$ and $m_{\tilde{g}}$, Philip Dießner checked the results up to permille accuracy by doing the calculation using \texttt{GoSam}\cite{Cullen:2014yla, Cullen:2011ac} and \texttt{MadGraph5\_aMC@NLO}\cite{Alwall:2014hca}.\\
The next-to-leading order cross sections of this chapter bear a relative uncertainty of one percent due to the numerical integration. The uncertainty which corresponds to the variation of the scales $\mu_R$ and $\mu_F$, see section \ref{sec:tree-level_cross_sections},  evaluate to $\approx$ 15\%.

@@

\begin{table}[H]
\begin{center}
\begin{tabular}{c|c?c|c|c?c|c|c}
\multicolumn{2}{c?}{} & \multicolumn{3}{c?}{$p + p \to \tilde{u}_L + \tilde{u}_R$} & \multicolumn{3}{c}{$p + p \to \tilde{u} + \tilde{u}$} \\
\hlinewd{2pt}
$m_{\tilde{q}}$ in GeV & $m_{\tilde{g}}$ in GeV & $\sigma^{\mathrm{LO}}$ in fb & $\sigma^{\mathrm{NLO}}$ in fb & $K$ & $\sigma^{\mathrm{LO}}$ in fb & $\sigma^{\mathrm{NLO}}$ in fb & $K$\\
\hlinewd{2pt}
$500$ & $500$ & $966.4$ & $1328$ & $1.37$ & $2333$ & $3102$ \ignore{1328+2*887} & $1.33$\\
$500$ & $1000$ & $303.4$ & $352$ & $1.16$ & $1271$ & $1393$ \ignore{353 + 2*520} & $1.10$\\
$1000$ & $1000$ & $42.63$ & $58.5$ & $1.37$ & $122.2$ & $161.3$ \ignore{58.5+2*51.4} & $1.32$\\
$1000$ & $2000$ & $11.56$ & $13.3$ & $1.15$ & $66.36$ & $72.1$ \ignore{13.3+2*29.4} & $1.09$\\
$1500$ & $3000$ & $0.9166$ & $1.05$ & $1.14$ & $7.045$ & $7.57$\ignore{1.05+2*3.26} & $1.07$
\end{tabular}
\caption{$K$-factors of the process $pp \to \tilde{u}_L\tilde{u}_R$ and $pp \to \tilde{u}\tilde{u}$, where \mbox{$\tilde{u}\tilde{u} \in \left\{ \tilde{u}_L\tilde{u}_R, \tilde{u}_L\tilde{u}_L, \tilde{u}_R\tilde{u}_R \right\}$,} in the MSSM for a selected set of masses. The used parton density functions are the same as in table \ref{tab:MRSSMKfactors}.}\label{tab:KfactorsMSSM}
\end{center}
\end{table}
\begin{figure}[H]
\begin{center}
\includegraphics[scale=.6]{figures/Kfactor_MSSM.png}
\caption{Contour plot of the $K$-factor of the process  $pp \to \tilde{u}_L\tilde{u}_R$ and $pp \to \tilde{u}\tilde{u}$, where \mbox{$\tilde{u}\tilde{u} \in \left\{ \tilde{u}_L\tilde{u}_R, \tilde{u}_L\tilde{u}_L, \tilde{u}_R\tilde{u}_R \right\}$,} in the MSSM. The used parton density functions are the same as in table \ref{tab:MRSSMKfactors}.}\label{fig:Kfactor_MSSM}
\end{center}
\end{figure}
Again, it is clearly visible that the $K$-factors depend rather strongly on the ratio $\frac{m_{\mathrm{g}}}{m_{\mathrm{q}}}$ but not that strongly on the masses themselves (see also fig. \ref{fig:Kfactor_MSSM}). As the real corrections are identical to those in the MRSSM, it is again these very real corrections which are responsible for an enhancement of the $K$-factor for large values of  $\frac{m_{\mathrm{g}}}{m_{\mathrm{q}}}$. This has also been found in \cite{Beenakker:1996ch}.
Comparing with the results from the MRSSM in table \ref{tab:MRSSMKfactors}, one can state that the $K$-factors of the MRSSM are slightly larger. This might be the case, as there are additional degrees of freedom in the $R$-symmetric model, namely the octino which enters the gluino self-energy contributions (see second diagram from the right in fig. \ref{fig:GluinoSE}) and sgluons which enter box diagrams (see lower right diagram in fig. \ref{fig:1loopdiagrams}). The dependence on the sgluon mass is discussed within the next section.\\
The uncertainties of next-to-leading order cross sections, due to the phase space integration, within this section are of percent order. The uncertainty which corresponds to the scale variation does not exceed 15\%.

### 2016-08-17 TreeLevel.tex
changes after submission

For consistency reasons also the stop is excluded from the final states. One therefore deals with $n_f-1 = 5$ quark flavors. In view of the renormalization and mass factorization to be performed at the one-loop level, the results are calculated in (conventional) dimensional regularization (see section \ref{sec:RegSchemes}) and are therefore given in $D = 4 - 2\epsilon$ dimensions. Furthermore it has been distinguished between the gauge coupling $g_s$ from the gluon-quark-quark vertex and its supersymmetric analogue $\hat{g}_s$ from the gluino-squark-quark vertex. So far, it has not been distinguished between them because supersymmetry dictates them to be identical. However, the loop corrections to their corresponding vertex differ in dimensional regularization by a finite amount, as will be shown in section \ref{sec:renMRSSM}. To rectify this, an additional finite (supersymmetry restoring) counterterm needs to be added to one of the renormalization constants of $g_s$ or $\hat{g}_s$. This will be done in \ref{sec:SUSYrestore}.\\

@@

&\beta_{\tilde{q}} = \sqrt{1-\frac{4 m_{\tilde{q}}^2}{s}} && \beta_{\tilde{g}} = \sqrt{1-\frac{4 m_{\tilde{g}}^2}{s}}\nonumber\\
&m_-^2 = m_{\tilde{g}}^2 - m_{\tilde{q}}^2 && \kappa = \sqrt{(s-m_{\tilde{g}}^2-m_{\tilde{q}}^2)^2-4m_{\tilde{g}}^2m_{\tilde{q}}^2}\nonumber\\
& L_1 = \ln \frac{s+2m_-^2 - s\beta_{\tilde{q}}}{s+2m_-^2 + s\beta_{\tilde{q}}} && L_2= \ln \frac{s - 2m_-^2 - s\beta_{\tilde{g}}}{s - 2m_-^2 + s\beta_{\tilde{g}}}\nonumber\\
& L_3 = \ln \frac{s - m_-^2 - \kappa}{s - m_-^2 + \kappa} && L_4= \ln \frac{s + m_-^2 - \kappa}{s + m_-^2 + \kappa}

@@

In the MRSSM only the production of ``chirality'' unlike squarks $\tilde{q}_L \tilde{q}_R$ is allowed whilst in the MSSM also ``chirality'' like squarks can be produced. This is again a consequence of the conservation of R-charge. The upshot of this is a suppression of squark production in the MRSSM in comparison to the MSSM. To be more explicit the suppression of squark production in the MRSSM grows with the gluino mass. This can be understood as follows: As in the MRSSM a left handed squark needs to be produced with a right handed squark one can read off, from the Feynman rules given in Appendix \ref{sec:FeynmanRules}, that the gluino propagator $i\frac{\slashed{p}+m_{\tilde{g}}}{p^2-m_{\tilde{g}}^2}$ is sandwiched between the projectors $P_L$ and $P_R$ which leads to the cancellation of the gluino mass in the numerator. Therefore for small momenta of the gluino compared to the gluino mass one gets $\mathcal{M}$ $\sim m_{\tilde{g}}^{-2}$ in the MRSSM while in the MSSM one finds a suppression proportional to $m_{\tilde{g}}^{-1}$.\\
When considering squark production, one has to sum $|\mathcal{M}|^2$ over all helicities. The diagrams for those different final state helicities are shown for flavor like squark production in tab. \ref{tab:squark_likeflavor} and for flavor unlike squark production in tab. \ref{tab:squark_unlikeflavor} for the MSSM and the MRSSM. To avoid double counting, one needs to weight $|\mathcal{M}|^2(qq\to \tilde{q}_L\tilde{q}_L)$ and $|\mathcal{M}|^2(qq\to \tilde{q}_R\tilde{q}_R)$ with a statistical factor of $\frac{1}{2}$ as one integrates over the momenta of both particles in $t$- and $u$-channel diagrams to arrive at the cross section.

@@

\caption{All Feynman diagrams contributing to flavor unlike squark production in the MSSM and the MRSSM for the example of $u$- and $d$-quarks.}\label{tab:squark_unlikeflavor}

>>>>

For consistency reasons also the stop is excluded from the final states. One therefore deals with $n_f-1 = 5$ quark flavors. In view of the renormalization and mass factorization to be performed at the one-loop level, the results are calculated in (conventional) dimensional regularization (see section \ref{sec:RegSchemes}) and are therefore given in $D = 4 - 2\epsilon$ dimensions. Furthermore it has been distinguished between the gauge coupling $g_s$ from the gluon-quark-quark vertex and its supersymmetric analogue $\hat{g}_s$ from the gluino-squark-quark vertex. So far, it has not been distinguished between them because supersymmetry dictates them to be identical. However, the loop corrections to their corresponding vertex differ in dimensional regularization by a finite amount, as will be shown in section \ref{sec:renMRSSM}. To rectify this, an additional finite (supersymmetry restoring) counterterm needs to be added to one of the renormalization constants of $g_s$ or $\hat{g}_s$. This will be done in section \ref{sec:SUSYrestore}.\\

@@

&\beta_{\tilde{q}} = \sqrt{1-\frac{4 m_{\tilde{q}}^2}{s}}, && \beta_{\tilde{g}} = \sqrt{1-\frac{4 m_{\tilde{g}}^2}{s}},\nonumber\\
&m_-^2 = m_{\tilde{g}}^2 - m_{\tilde{q}}^2, && \kappa = \sqrt{(s-m_{\tilde{g}}^2-m_{\tilde{q}}^2)^2-4m_{\tilde{g}}^2m_{\tilde{q}}^2},
\nonumber\\
& L_1 = \ln \frac{s+2m_-^2 - s\beta_{\tilde{q}}}{s+2m_-^2 + s\beta_{\tilde{q}}}, && L_2= \ln \frac{s - 2m_-^2 - s\beta_{\tilde{g}}}{s - 2m_-^2 + s\beta_{\tilde{g}}}, \nonumber\\
& L_3 = \ln \frac{s - m_-^2 - \kappa}{s - m_-^2 + \kappa}, && L_4= \ln \frac{s + m_-^2 - \kappa}{s + m_-^2 + \kappa}

@@

In the MRSSM only the production of ``chirality'' unlike squarks $\tilde{q}_L \tilde{q}_R$ is allowed whilst in the MSSM also ``chirality'' like squarks can be produced. This is again a consequence of the conservation of $R$-charge. The upshot of this is a suppression of squark production in the MRSSM in comparison to the MSSM. To be more explicit the suppression of squark production in the MRSSM grows with the gluino mass. This can be understood as follows: As in the MRSSM a left handed squark needs to be produced with a right handed squark, one can read off, from the Feynman rules given in Appendix \ref{sec:FeynmanRules}, that the gluino propagator $i\frac{\slashed{p}+m_{\tilde{g}}}{p^2-m_{\tilde{g}}^2}$ is sandwiched between the projectors $P_L$ and $P_R$ which leads to the cancellation of the gluino mass in the numerator. Therefore for small momenta of the gluino compared to the gluino mass one gets $\mathcal{M}$ $\sim m_{\tilde{g}}^{-2}$ in the MRSSM while in the MSSM one finds a suppression proportional to $m_{\tilde{g}}^{-1}$.\\
When considering the total cross section, one has to sum $|\mathcal{M}|^2$ over all helicities. The diagrams for those different final state helicities are shown for flavor like squark production in tab. \ref{tab:squark_likeflavor} and for flavor unlike squark production in tab. \ref{tab:squark_unlikeflavor} for the MSSM and the MRSSM. To avoid double counting, one needs to weight $|\mathcal{M}|^2(qq\to \tilde{q}_L\tilde{q}_L)$ and $|\mathcal{M}|^2(qq\to \tilde{q}_R\tilde{q}_R)$ with a statistical factor of $\frac{1}{2}$ as one integrates over the momenta of both particles in $t$- and $u$-channel diagrams to arrive at the cross section.

@@

\caption{All Feynman diagrams contributing to flavor unlike squark production in the MSSM and the MRSSM for the example of the initial state with $u$- and $d$-quarks.}\label{tab:squark_unlikeflavor}

### 2016-08-17 Virt_Real.tex
changes after submission

\section{Virtual and Real Corrections}\label{sec:VirtRealCorr}
The results calculated in the previous chapter are not the complete theoretical predictions for the cross sections of the various processes but only the first term in a perturbation series of $\alpha_s$.\\
To provide accurate predictions, it is necessary that corrections to the leading order are small. This implies that $\alpha_s$, which is strongly dependent on the energy scale, needs to fulfill $\alpha_s < 1$. It is known that $\alpha_s$ becomes of $\mathcal{O}(1)$ and larger when the energy scale is of $\mathcal{O}(\unit[200]{MeV})$ and smaller\cite{dissertori2003quantum}. Fortunately squark production is a process which involves large enough energy to maintain the validity of perturbation theory, as the typical energy scale involved, is the mass of squarks which certainly fulfills $m_{\tilde{q}} > \unit[500]{GeV}$.\\
This section describes the necessary steps in the calculation of the squark production cross section at next-to-leading order, i.e. its $\mathcal{O}(\alpha_s)$-correction.\\
\ignore{Reason validity of perturbation theory in this context.}

>>>>

\section{Virtual and Real Corrections}\label{sec:VirtRealCorr}
The results calculated in the previous chapter are not the complete theoretical predictions for the cross sections of the various processes but only the first term in a perturbation series of $\alpha_s$.\\
To provide accurate predictions, it is necessary that corrections to the leading order are small. This implies that $\alpha_s$, which is strongly dependent on the energy scale, needs to fulfill $\alpha_s < 1$. It is known that $\alpha_s$ becomes of $\mathcal{O}(1)$ and larger when the energy scale is of $\mathcal{O}(\unit[200]{MeV})$ and smaller\cite{dissertori2003quantum}. Fortunately, squark production is a process which involves large enough energy to maintain the validity of perturbation theory, as the typical energy scale involved, is the mass of squarks which certainly fulfills $m_{\tilde{q}} > \unit[500]{GeV}$.\\
This section describes the necessary steps in the calculation of the squark production cross section at next-to-leading order, i.e. its $\mathcal{O}(\alpha_s)$-correction.\\
\ignore{Reason validity of perturbation theory in this context.}
